### 2024-03-05 doc/15yrsChange.Rmd
Update 15yrsChange.Rmd
worked on results paragraphs for first 5 figures

Woody mortality was the largest driver of the negative trend in biomass, and certain species were responsible for higher levels of mortality. Fraxinus americana had the highest abovegroung woody mortality rates of any species present on the plot, peaking at **VALUE** Mg C/ha/year lost in *2020* , and **VALUE** Mg C/ha/year lost in 2022 (Figure 4). Quercus velutina contributed the second-highest levels of mortality, losing **VALUE** Mg C/ha/year in 2022. Quercus rubra, Carya species, Quercus prinus, Quercus alba, and Liriodendron tulipifera were all significant contributors as well.

## Species compositon of recruitment flux

>>>>

Woody mortality was the largest driver of the negative trend in biomass, and certain species were responsible for higher levels of mortality. Fraxinus americana had the highest aboveground woody mortality rates of any species present on the plot, peaking at **VALUE** Mg C/ha/year lost in *2020* , and **VALUE** Mg C/ha/year lost in 2022 (Figure 4). Quercus velutina contributed the second-highest levels of mortality, losing **VALUE** Mg C/ha/year in 2022. Quercus rubra, Carya species, Quercus prinus, Quercus alba, and Liriodendron tulipifera were all significant contributors as well.

## Species compositon of recruitment flux
Certain species dominated aboveground woody recruitment, with understory species being recruited at higher rates than canopy species (Figure 5). Out of the canopy species, Carya species showed the highest levels of recruitment with a rate of **VALUE** Mg C/ha/year recruited from 2018 to 2023 (Figure 5a). Acer negundo had the second highest rate of recruitment for canopy species at **VALUE** Mg C/ha/year from 2018 to 2023. Fagus grandifolia, Fraxinus americana, and Ulmus rubra are the other species with the highest recruitment rates. Most canopy species had lower recruitment rates in the 2018 to 2023 census interval than the 2008 to 2013 interval. Lindera benzoin had by far the highest recruitment rate of the understory species at **VALUE** Mg C/ha/year from 2018 to 2023 (Figure 3b). Asimina triloba had the second highest rate of recruitment of the understory species at **VALUE** Mg C/ha/year recruited from 2018 to 2023. Other understory species with high recruitment were Carpinus caroliniana, Hamamelis virginiana, and Celtis occidentalis.
